\documentclass[12pt]{beamer}
\beamertemplatenavigationsymbolsempty
\usetheme{Madrid}
\usepackage[utf8]{inputenc}
\usepackage{enumitem}
\usepackage{ulem}

\title{\textbf{DIAMONDS}}
\author[Bvrith]{Y.Vijitha 20WH1A0483 ECE-B\\K.Sai Tejaswi 20WH1A1206 IT-A\\ B.Nandini 20WH1A0514 CSE-A\\ T.Harshitha 20WH1A6637 CSE-AI&ML\\ Ch.Abitha 20WH1A0440 ECE-A}
\date{\textbf{23rd October, 2021}}


\begin{document}
    \begin{frame}
        \titlepage
    \end{frame}
	    \begin{frame}
	\frametitle{Day4}
	\begin{itemize}
	    \item K.Sai Tejaswi worked on comparing bidding cards of player1, player2 and player3, allocating score to players and declaring winner.
	    \item B.Nandhini worked on display of diamond cards.
	    \item Vijitha worked on integrating the title screen and the game window.
	    \item Harshitha worked on sound effects for the card movements.
	    \item Abitha added background music to the game.
	    \end{itemize}
	    \end{frame}
    \begin{frame}
        \frametitle{Learnings}
	\begin{itemize}
	    \item We got to know about implementation of UI applications. We have used functions and classes while writing code. 
	\end{itemize}
    \end{frame}
    \begin{frame}
	\frametitle{Challenges}
        \begin{itemize}
	    \item We are trying to understand how to link UI with game code. We faced difficulty in designing game whether the game screen should be visible on only one system or should implement it as in online format
        \end{itemize}
    \end{frame}
    \begin{frame}
	\frametitle{Statistics}
        \begin{itemize}
        \item K.Sai Tejaswi\\
	     \item Number of Lines of Code:58\\
	     \item Number of Functions:2\\
	     \item T.Harshitha\\
	     \item Number of Lines of Code:16\\
	     \item Number of Functions:3\\
	     \item Y.Vijitha\\
	     \item Number of Lines of Code:49\\
	     \item Number of Functions:3\\
	     \item B.Nandhini\\
	     \item Number of Lines of Code:23\\
	     \item Number of Functions:2\\
	     \item CH.Abitha\\
	     \item Number of Lines of Code:21\\
	     \item Number of Functions:1\\
	     
	     
        \end{itemize}
    \end{frame}
    \begin{frame}
	\begin{center}
	      THANK YOU
	\end{center}
    \end{frame}
\end{document}

