\documentclass[12pt]{beamer}
\beamertemplatenavigationsymbolsempty
\usetheme{Madrid}
\usepackage[utf8]{inputenc}
\usepackage{enumitem}
\usepackage{ulem}

\title{\textbf{DIAMONDS}}
\author[Bvrith]{Y.Vijitha 20WH1A0483 ECE-B\\K.Sai Tejaswi 20WH1A1206 IT-A\\ B.Nandini 20WH1A0514 CSE-A\\ T.Harshitha 20WH1A6637 CSE-AI&ML\\ Ch.Abitha 20WH1A0440 ECE-A}
\date{\textbf{24th October, 2021}}


\begin{document}
    \begin{frame}
        \titlepage
    \end{frame}
	    \begin{frame}
	\frametitle{Day5}
	\begin{itemize}
	    \item K.Sai Tejaswi worked on adding functions to the game code.
	    \item B.Nandhini worked on displaying diamond cards on the game window.
	    \item Vijitha worked on displaying the cards of player2 and player3 on the game window.
	    \item Harshitha worked on displaying player1 cards on the game window.
	    \item Abitha worked on the end screen and scores of the players.
	    \end{itemize}
	    \end{frame}
    \begin{frame}
        \frametitle{Learnings}
	\begin{itemize}
	    \item We got to know about implementation of UI applications. We have used functions and classes while writing code. 
	\end{itemize}
    \end{frame}
    \begin{frame}
	\frametitle{Challenges}
        \begin{itemize}
	    \item We are trying to understand how to link UI with game code. We faced difficulty in designing game whether the game screen should be visible on only one system or should implement it as in online format
        \end{itemize}
    \end{frame}
    \begin{frame}
	\frametitle{Statistics}
        \begin{itemize}
        \item K.Sai Tejaswi\\
	     \item Number of Lines of Code:53\\
	     \item Number of Functions:2\\
	     \item T.Harshitha\\
	     \item Number of Lines of Code:39\\
	     \item Number of Functions:3\\
	     \item Y.Vijitha\\
	     \item Number of Lines of Code:32\\
	     \item Number of Functions:3\\
	     \item B.Nandhini\\
	     \item Number of Lines of Code:23\\
	     \item Number of Functions:2\\
	     \item CH.Abitha\\
	     \item Number of Lines of Code:21\\
	     \item Number of Functions:1\\
	     
	     
        \end{itemize}
    \end{frame}
    \begin{frame}
	\begin{center}
	      THANK YOU
	\end{center}
    \end{frame}
\end{document}